### 2018-05-25 msc_diploma_cubesat_galgoczi.tex
tt

The build up of the satellite is quite complex, consisiting of 9 modules, each with a specific material composition. Therefore the CAD model of the satellite was imported into Geant4 in order to understand how the satellite itself would affect the measurements. The "calibrated" scintillator afterwards was placed on the side of the satellite.

@@

We are designing a fleet of nanosatellites to perform accurate position determinations
of short-duration gamma-ray bursts by measuring arrival time differences.
To achieve sufficient photon statistics to measure the arrival times
precisely under the severe limitations of size, mass, and power consumption,
we propose the use of a large-area CsI scintillator that has high light output
and the use of a small-sized multipixel photon counter (MPPC) that has low
power consumption. We plan to use one of the latest-model MPPCs provided
by Hamamatsu Photonics, which has an active area of 6  6 mm2. We have compared the performance of two scintillators of different sizes (150 75  5 mm3 and 100  75  5 mm3); the bigger one is the maximum size that can be mounted on a three-unit satellite, according to CubeSat standards.
We have found that the two scintillators have similar light yields and each has an energy threshold of $\sim$10 keV at 25C. We have also examined the position dependence of the light yield by using radiation from 241Am (59.5 keV) source, and have confirmed that uniformity was improved by using two MPPCs for signal readout.

@@

\begin{figure}[h!]
\includegraphics[width=150.0mm]{images/irradiation.png}
\caption{The $^{241}$Am $gamma$ source was placed in a collimator system as can be seen on the image}
\end{figure}

@@

The geometry of the two channel read out setup was simulated

\begin{figure}[h!]
\centering
\includegraphics[width=160.0mm]{images/2channel.png}
\caption{Simulation of 100 $\gamma$s emitted from the source. The blue lines represent the track of the $\gamma$s and the green lines represent the track of the optical photons created by scintillation. Only the photons that were detected are drawn.}
\label{fig:sim_setup}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=150.0mm]{images/satellite_rad.png}
\caption{The satellite radiated by a pencil beam of 10.000 $\gamma$ particles. The scattered $\gamma$s induce signal in the scintillator}
\end{figure}

\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c|c|c|} 
 \hline
 Name of module & mass [g] & Type of material & Mass ratio [\%]\\\hline
 ADCS &	710	& Aluminum 6061-T6 &	50\\
			& & Copper Electric	& 25 \\
			& &  Glass Borosilicate 	& 25\\\hline
COM	& 	90	& 	Stainless Steel 	& 2\\
			& 	& Brass Generic		& 25\\
			& 	& Aluminum 7075-T73		& 40\\
			& 	& FR4 Glass-Epoxy sheet	& 	33\\\hline
EPS	& 	750	& 	FR4 Glass-Epoxy sheet		& 25\\
			& 	& Aluminum 6061-T6		& 75\\\hline
OBC	&	50		& FR4 Glass-Epoxy sheet	& 	100\\\hline
STRU	& 	980		& Aluminum 6061-T6	& 	100\\\hline
SP	& 	570		& Solar Panel	& 	100\\\hline
Payload	& 	1100	& 	As you wish	& 	100\\
 \hline
\end{tabular}
\end{center}
\caption{The mass ratio of materials that are used for the satellite}
\end{table}

\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c|c|c|c|} 
 \hline
%Material name & El. 1	& El. 1 m.r. & El. 2 & El. 2 m.r. &El.3	& El. 3 m.r. &El. 4	& El. 4 m.r. &El.	5& El. 5 m.r. &El.	6& El. 6 m.r. \\\hline
Material name & &&&&&&&&&&& \\\hline

Aluminum 6061-T6 &	Al & 96.90 &	Mg &	1.20 &	Si &	0.80 &	Fe &	0.70 &	Cu &	0.40 & &\\\hline		
Aluminum 7075-T73 &	Al &	88.60 &	Zn &	6.10 &	Mg &	2.90 &	Cu &	2.00 &	Si &	0.40 & &\\\hline		
%Stainless Steel A2-70  AISI 304 (EN 1.4301) &	Fe &	66.50 &	Cr &	20.00 &	Ni &	10.50	Mn &	2.00 &	Si &	1.00 & &\\\hline		
Stainless Steel &	Fe &	66.50 &	Cr &	20.00 &	Ni &	10.50	&Mn &	2.00 &	Si &	1.00 & &\\\hline		
Copper Electric  &Cu &	100.00 & & & & & & & & & &	\\\hline					
Glass Borosilicate &	Si &	42.10 &	O &	54.80 &	B &	3.10 & & & & & &\\\hline			
FR4 Glass-Epoxy &	Si &	23.39 &	O &	36.02 &	C &	37.04 &	H &	3.55 & & & &\\\hline		
Brass Generic &	Cu &	85.00 &	Zn &	15.00 & & & & & & & &\\\hline						
Solar Panel &	Ge &	38.00 &	Si &	24.00 &	O &	20.00 &	C &	13.00 &	H &	4.00 &	B &	1.00\\\hline
\end{tabular}
\end{center}
\caption{The chemical composition of materials that are used for the satellite}
\end{table}

@@

A lead sheet was drilled with nine holes to collimate the $\gamma$ source to certain parts of the scintillator. These measurements were carried out by Kento Torigoe at the University of Hiroshima. This configuration with a lead sheet was built up in Geant4 (fig. \ref{fig:sim_setup} and 3.6 million $\gamma$s were simulated at each position.

@@

%ADC / energy calibration from measurement 20170829 illetve az egy chanellel: grb\_status3

\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c| } 
\hline
Refl:& 0.995 & Abs.:& 50 cm   &  &  &  &  &  &  \\ 
\hline
 Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
 Pos. of main peak & 0.4013 & 0.3917 & 0.3981 & 0.4045 & 0.4172 & 0.4140 & 0.2580 & 1 & 0.2739\\ 
 \hline   
\hline
 Refl:& 0.997 & Abs.:& 60 cm   &  &  &  &  &  &  \\ 
 \hline
  Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
  Pos. of main peak & 0.4588 & 0.4587 & 0.4697 & 0.4734 & 0.4700 & 0.4737 & 0.3388 & 1 & 0.3365  \\ 
 \hline \hline
Refl:& 0.999 & Abs.:& 80 cm   &  &  &  &  &  &  \\ 
 \hline
  Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
  Pos. of main peak &  &  &  &  &  &  &  & 1 &   \\ 
 \hline \hline
Refl:& 0.9996 & Abs.:& 80 cm   &  &  &  &  &  &  \\ 
 \hline
  Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
  Pos. of main peak &  &  &  &  &  &  &  & 1 &  \\ 
  \hline \hline
Refl:& 0.9999 & Abs.:& 105 cm   &  &  &  &  &  &  \\ 
 \hline
  Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
  Pos. of main peak & 0.6911 & 0.6865 & 0.6956 & 0.7002 & 0.6956 & 0.7002 & 0.6041 & 1 & 0.5955 \\ 
  \hline
\end{tabular}
 \caption{The position of the Gaussian peak fitted to the 60 keV peak of the Am source for several irradiated positions}
 \label{tabl:simulated}
\end{center}
\end{table}

\subsubsection{Calibration of photon yield}

@@

\begin{figure}[h!]
\includegraphics[width=150.0mm]{images/calibration_photon_yield.png}[H!]
\caption{The spectra of 11 million photons taken experimentally (blue histogram) matched up with the results of the simulation (green histogram) and the Gaussian fitted to the simulated data}
\end{figure}

@@

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=0.45\textwidth,origin=c,angle=0]{images/gamma0mac.png}
 \qquad
 \includegraphics[width=.45\textwidth,origin=c]{images/gamma17mac.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:band500e}  }
 \end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=130.0mm]{images/gammashittingsat.png}
\label{eq:bandfunc}
\end{center}
\end{figure}

@@

Electrons
'Trapped electron model: AE-8 MIN'
%'Energy','MeV','Energy'
%'IFlux','cm^-2 s^-1','Integral Flux'
%'DFlux','cm^-2 s^-1 MeV^-1','Differential Flux'

The AE-8 model was used in SPENVIS to obtain the spatially avaraged elextron energy spectra for an altitude of 500 km both for solar minimum and maximum. The inclination of the orbit was chosen to be 89 $^{\circ}$. At the moment hadron resonances are not taken into account in the simulation.

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.45\textwidth,origin=c,angle=0]{images/alt_500km_AP-8_MIN_averaged_spectra.png}
 \qquad
 \includegraphics[width=.45\textwidth,origin=c]{images/alt_500km_AP-8_MAX_averaged_spectra.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:band500p} The spatially avaraged band function (differential flux for a given energy band, solid line) and the integrated band function (dotted line) of protons at an altitude of 500 km for solar minimum (left) and solar maximum (right) }
 \end{figure}

\begin{figure}[h!]
\centering % \begin{center}/\end{center} takes some additional vertical space
\includegraphics[width=.55\textwidth,origin=c,angle=0]{images/electrons0degspectra.png}
\qquad
\includegraphics[width=.4\textwidth,origin=c,angle=90]{images/0mac.png} 
% "\includegraphics" from the "graphicx" permits to crop (trim+clip)
% and rotate (angle) and image (and much more)
\caption{\label{fig:i} The spectrum measured when the electrons were shot perpendicular to the scintillator (called angle of 0 $^{\circ}$)}
\end{figure}

\begin{figure}[h!]
\centering % \begin{center}/\end{center} takes some additional vertical space
\includegraphics[width=.3\textwidth,origin=c,angle=0]{images/satellite.png}
\qquad
\includegraphics[width=.5\textwidth,origin=c,angle=90]{images/8mac.png} 
% "\includegraphics" from the "graphicx" permits to crop (trim+clip)
% and rotate (angle) and image (and much more)
\caption{\label{fig:i} The CAD model of the satellite (on the right) and the view of the imported model in Geant (on the left)}
\end{figure}

@@

The results show...

Fourthly, the effect of cosmic radiation was invastigated by utilizing the energy spectra of cosmic protons and electrons at the altitude of 500km. The satellite was radiated by these particles in Geant4 in the same positions that were used for the $\gamma$-rays of GRB 9900123. The induced signal of these particles was determined. This needs to be minimalized as it "competes" with the signal of gamma particles from GRBs.

>>>>

The build up of the satellite is quite complex, consisiting of 7 modules, each with a specific material composition. Therefore the CAD model of the satellite was imported into Geant4 in order to understand how the satellite itself would affect the measurements. The "calibrated" scintillator afterwards was placed on the side of the satellite.

@@

%We are designing a fleet of nanosatellites to perform accurate position determinations of short-duration gamma-ray bursts by measuring arrival time differences. To achieve sufficient photon statistics to measure the arrival times precisely under the severe limitations of size, mass, and power consumption, we propose the use of a large-area CsI scintillator that has high light output and the use of a small-sized multipixel photon counter (MPPC) that has low power consumption. We plan to use one of the latest-model MPPCs provided by Hamamatsu Photonics, which has an active area of 6  6 mm2. We have compared the performance of two scintillators of different sizes (150 75  5 mm3 and 100  75  5 mm3); the bigger one is the maximum size that can be mounted on a three-unit satellite, according to CubeSat standards. We have found that the two scintillators have similar light yields and each has an energy threshold of $\sim$10 keV at 25C. We have also examined the position dependence of the light yield by using radiation from 241Am (59.5 keV) source, and have confirmed that uniformity was improved by using two MPPCs for signal readout.

@@

\begin{figure}[h!]
\includegraphics[width=150.0mm]{images/irradiation.png}
\caption{The $^{241}$Am $gamma$ source was placed in a collimator system as can be seen on the image}
\label{fig:this_set}
\end{figure}

@@

In order to simulate the satellite with the two channel read out setup, first this configuration was tested. The simulation of this setup can be seen in fig. \ref{fig:sim2ch}. The $\gamma$ source was collimated with a lead sheet that was drilled. The optical photons that were detected are shown only. The two read volumes correspond to the MPPCs.

\begin{figure}[h!]
\centering
\includegraphics[width=130.0mm]{images/2channel.png}
\caption{Simulation of 100 $\gamma$s emitted from the source. The blue lines represent the track of the $\gamma$s and the green lines represent the track of the optical photons created by scintillation. Only the photons that were detected are drawn.}
\label{fig:sim2ch}
\end{figure}

@@

\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c|c|c|} 
 \hline
 Name of module & mass [g] & Type of material & Mass ratio [\%]\\\hline
 ADCS &	710	& Aluminum 6061-T6 &	50\\
			& & Copper Electric	& 25 \\
			& &  Glass Borosilicate 	& 25\\\hline
COM	& 	90	& 	Stainless Steel 	& 2\\
			& 	& Brass Generic		& 25\\
			& 	& Aluminum 7075-T73		& 40\\
			& 	& FR4 Glass-Epoxy sheet	& 	33\\\hline
EPS	& 	750	& 	FR4 Glass-Epoxy sheet		& 25\\
			& 	& Aluminum 6061-T6		& 75\\\hline
OBC	&	50		& FR4 Glass-Epoxy sheet	& 	100\\\hline
STRU	& 	980		& Aluminum 6061-T6	& 	100\\\hline
SP	& 	570		& Solar Panel	& 	100\\\hline
Payload	& 	100	& 	Aluminum 7075-T73	& 	100\\
 \hline
\end{tabular}
\end{center}
\caption{The mass ratio of materials that are used for the satellite}
\label{table:materials}

\end{table}

The material composition of the satellite can not be exported to Geant4 from CAD files directly. Therefore an avarage material composition was calculated for all the modules. In table $\ref{table:materials}$ the material composition of the 7 modules are listed. These materials, mostly alloys consist of several elements. The Geant4 cross section database is built up for elements. Therefore these materials had to be broken down to elements.

\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c|c|c|c|} 
 \hline
%Material name & El. 1	& El. 1 m.r. & El. 2 & El. 2 m.r. &El.3	& El. 3 m.r. &El. 4	& El. 4 m.r. &El.	5& El. 5 m.r. &El.	6& El. 6 m.r. \\\hline
Material name & &&&&&&&&&&& \\\hline
Aluminum 6061-T6 &	Al & 96.90 &	Mg &	1.20 &	Si &	0.80 &	Fe &	0.70 &	Cu &	0.40 & &\\\hline		
Aluminum 7075-T73 &	Al &	88.60 &	Zn &	6.10 &	Mg &	2.90 &	Cu &	2.00 &	Si &	0.40 & &\\\hline		
%Stainless Steel A2-70  AISI 304 (EN 1.4301) &	Fe &	66.50 &	Cr &	20.00 &	Ni &	10.50	Mn &	2.00 &	Si &	1.00 & &\\\hline		
Stainless Steel &	Fe &	66.50 &	Cr &	20.00 &	Ni &	10.50	&Mn &	2.00 &	Si &	1.00 & &\\\hline		
Copper Electric  &Cu &	100.00 & & & & & & & & & &	\\\hline			
Glass Borosilicate &	Si &	42.10 &	O &	54.80 &	B &	3.10 & & & & & &\\\hline			
FR4 Glass-Epoxy &	Si &	23.39 &	O &	36.02 &	C &	37.04 &	H &	3.55 & & & &\\\hline		
Brass Generic &	Cu &	85.00 &	Zn &	15.00 & & & & & & & &\\\hline						
Solar Panel &	Ge &	38.00 &	Si &	24.00 &	O &	20.00 &	C &	13.00 &	H &	4.00 &	B &	1.00\\\hline
\end{tabular}
\end{center}
\caption{The chemical composition of materials in mass fraction that are used for the satellite}
\end{table}

In fig. \ref{fig:sat_rad} the simulation of the satellite and the two channel read out setup can be seen. 100 $\gamma$ particles were used to shoot the satellite with a beam parralel to the plane of the scintillator. A scattered $\gamma$ particle can be seen being scattered into the scintillator and being detected.

\begin{figure}[h!]
\includegraphics[width=150.0mm]{images/satellite_rad.png}
\caption{The satellite radiated by a parallel beam of 100 $\gamma$ particles. The scattered $\gamma$s induce signal in the detector.}
\end{figure}
\label{fig:sat_rad}

@@

A lead sheet was drilled with nine holes to collimate the $\gamma$ source to certain parts of the scintillator. These measurements were carried out by Kento Torigoe at the University of Hiroshima. This configuration with a lead sheet was built up in Geant4 (fig. \ref{fig:this_set} and 3.6 million $\gamma$s were simulated at each position.

@@

%ADC / energy calibration from measurement 20170829 illetve az egy chanellel: grb\_status3 
\begin{center}

\begin{table}[h!]
\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c| } 
\hline
Refl:& 0.995 & Abs.:& 50 cm   &  &  &  &  &  &  \\ 
\hline
 Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
 Pos. of main peak & 0.4013 & 0.3917 & 0.3981 & 0.4045 & 0.4172 & 0.4140 & 0.2580 & 1 & 0.2739\\ 
 \hline   
\hline
 Refl:& 0.997 & Abs.:& 60 cm   &  &  &  &  &  &  \\ 
 \hline
  Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
  Pos. of main peak & 0.4588 & 0.4587 & 0.4697 & 0.4734 & 0.4700 & 0.4737 & 0.3388 & 1 & 0.3365  \\ 
 \hline \hline
Refl:& 0.999 & Abs.:& 80 cm   &  &  &  &  &  &  \\ 
 \hline
  Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
  Pos. of main peak &  &  &  &  &  &  &  & 1 &   \\ 
 \hline \hline
Refl:& 0.9996 & Abs.:& 80 cm   &  &  &  &  &  &  \\ 
 \hline
  Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
  Pos. of main peak &  &  &  &  &  &  &  & 1 &  \\ 
  \hline \hline
Refl:& 0.9999 & Abs.:& 105 cm   &  &  &  &  &  &  \\ 
 \hline
  Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
  Pos. of main peak & 0.6911 & 0.6865 & 0.6956 & 0.7002 & 0.6956 & 0.7002 & 0.6041 & 1 & 0.5955 \\ 
  \hline
\end{tabular}
 \caption{The position of the Gaussian peak fitted to the 60 keV peak of the Am source for several irradiated positions. The last set of parameters fit the experimental data.}
 \label{tabl:simulated}
\end{table}
\end{center}

\subsubsection{Calibration of the photon yield}

@@

\begin{figure}[h!]
\includegraphics[width=150.0mm]{images/calibration_photon_yield.png}[H!]
\caption{The spectra of 11 million photons taken experimentally (blue histogram) matched up with the results of the simulation (green histogram) and the Gaussian fitted to the simulated data}
\label{fig:sim_res_calib}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=130.0mm]{images/gammashittingsat.png}
\label{eq:diffpos}
\caption{The number of detections from the 10.000 $\gamma$ shoot in the simulation depending on the position of the GRB with respect to the longitudinal axis of the satellite.}
\end{center}
\end{figure}

As one expects the most $\gamma$s ($\sim$ 200) are detected when these particles hit the scintillator directly, with a perpendicular direction to the surface of the satellite. The effective area of the scintillator is the largest in this case and the $\gamma$s are not absorbed by the material of the satellite.

The worst case scenario is then the $\gamma$s hit the satellite with a direction parallel with the plane of the scintillator. Although some detections ($\sim$ 20) occur even in this case because $\gamma$s that scatter in the material of the satellite can be detected. In fig. \ref{fig:diffpos} one can see the number of detections from 10.000 $\gamma$s shot at the detector for a given position of the GRB.

In fig. $\ref{fig:mac17hits}$ one can see the comparison between the energy spectrum measured when the $\gamma$s hit the scintillator with a perpendicular direction and when they hit the satellite from behind. The difference between these two scenarious is that $\gamma$s had to travel through the material of the satellite in the second case. About 60 \% of gammas are lost do the absorption of the satellite.

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=0.45\textwidth,origin=c,angle=0]{images/gamma0mac.png}
 \qquad
 \includegraphics[width=.45\textwidth,origin=c]{images/gamma17mac.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{The measured spectrum when the $\gamma$s had to pass through the material of the satellite (right) and when they hit the scintillator directly (left)  \label{fig:mac17hits}}
 \end{figure}

@@

%'Energy','MeV','Energy'
%'IFlux','cm^-2 s^-1','Integral Flux'
%'DFlux','cm^-2 s^-1 MeV^-1','Differential Flux'

The AE-8 model was used in SPENVIS to obtain the spatially avaraged elextron energy spectra for an altitude of 500 km both for solar minimum and maximum. The inclination of the orbit was chosen to be 89 $^{\circ}$. %At the moment hadron resonances are not taken into account in the simulation.

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.45\textwidth,origin=c,angle=0]{images/alt_500km_AP-8_MIN_averaged_spectra.png}
 \qquad
 \includegraphics[width=.45\textwidth,origin=c]{images/alt_500km_AP-8_MAX_averaged_spectra.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:electrs} The spatially avaraged band function (differential flux for a given energy band, solid line) and the integrated band function (dotted line) of protons at an altitude of 500 km for solar minimum (left) and solar maximum (right) }
 \end{figure}

The integrated and differential spectra of electrons can be seen in fig. \ref{fig:electrs}. For the simulation the worst case scenario, the spectrum at solar maximum was utilized. Fig. \ref{fig:iii} shows the energy spectrum for the simulation of 0$^{\circ}$ when electrons hit the scintillator with a perpendicular direction.

\begin{figure}[h!]
\centering % \begin{center}/\end{center} takes some additional vertical space
\includegraphics[width=.55\textwidth,origin=c,angle=0]{images/electrons0degspectra.png}
\qquad
\includegraphics[width=.4\textwidth,origin=c,angle=90]{images/0mac.png} 
% "\includegraphics" from the "graphicx" permits to crop (trim+clip)
% and rotate (angle) and image (and much more)
\caption{\label{fig:iii} The spectrum measured when the electrons were shot perpendicular to the scintillator (called angle of 0 $^{\circ}$)}
\end{figure}

The total flux from the spectrum taken from SPENVIS (fig. \ref{fig:electrs})for 1 s and a cm$^{2}$ was 2.695.370.

@@

Fourthly, the effect of cosmic radiation was invastigated by utilizing the energy spectra of cosmic electrons at the altitude of 500km. The satellite was radiated by these particles in Geant4 in the same positions that were used for the $\gamma$-rays of GRB 9900123. The induced signal of these particles was determined. This needs to be minimalized as it "competes" with the signal of gamma particles from GRBs.

The results of the simulation of the full satellite shows that the satellite is clearly capable of detecting a GRB with a high signal to noise ratio. The effect of absorption can reduce the light yield by 60 \%. The effect of the electron background was also quantified. It is negligable with comparison to the signal induced by the $\gamma$ of the GRBs.
